---
title: "07 Sparklyr ML"
output: html_notebook
---

## Load Data

```{r}
library(sparklyr)
library(ggplot2)
library(dplyr)

sc <- spark_connect(master = "local")
```

```{r}

iris_tbl <- copy_to(sc, iris, "iris", overwrite = TRUE)
iris_tbl

```

Function                          Description
ml_kmeans	                        K-Means Clustering
ml_linear_regression	            Linear Regression
ml_logistic_regression	          Logistic Regression
ml_survival_regression	          Survival Regression
ml_generalized_linear_regression	Generalized Linear Regression
ml_decision_tree	                Decision Trees
ml_random_forest	                Random Forests
ml_gradient_boosted_trees	        Gradient-Boosted Trees
ml_pca	                          Principal Components Analysis
ml_naive_bayes	                  Naive-Bayes
ml_multilayer_perceptron	        Multilayer Perceptron
ml_lda	                          Latent Dirichlet Allocation
ml_one_vs_rest	                  One vs Rest



## K-MEANS CLUSTERING

```{r}

# kmeans_model <- ml_kmeans(iris_tbl, k = 3, features = c("Petal_Length", "Petal_Width"))

kmeans_model <- iris_tbl %>%
  ml_kmeans(k = 3, features = c("Petal_Length", "Petal_Width"))

kmeans_model

```

prediksi

```{r}

# predicted <- ml_predict(kmeans_model, iris_tbl) %>% collect

predicted <- kmeans_model %>%
  ml_predict(iris_tbl) %>% 
  collect
  
table(predicted$Species, predicted$prediction)

```

plot

```{r}

ml_predict(kmeans_model) %>%
  collect() %>%
  ggplot(aes(Petal_Length, Petal_Width)) +
  geom_point(aes(Petal_Width, Petal_Length, col = factor(prediction + 1)),
             size = 2, alpha = 0.5) + 
  geom_point(data = kmeans_model$centers, aes(Petal_Width, Petal_Length),
             col = scales::muted(c("red", "green", "blue")),
             pch = 'x', size = 12) +
  scale_color_discrete(name = "Predicted Cluster",
                       labels = paste("Cluster", 1:3)) +
  labs(
    x = "Petal Length",
    y = "Petal Width",
    title = "K-Means Clustering",
    subtitle = "Use Spark.ML to predict cluster membership with the iris dataset."
  )

```

## LINEAR REGRESSION

```{r}

lm_model <- iris_tbl %>%
  select(Petal_Width, Petal_Length) %>%
  ml_linear_regression(Petal_Length ~ Petal_Width)

iris_tbl %>%
  select(Petal_Width, Petal_Length) %>%
  collect %>%
  ggplot(aes(Petal_Length, Petal_Width)) +
    geom_point(aes(Petal_Width, Petal_Length), size = 2, alpha = 0.5) +
    geom_abline(aes(slope = coef(lm_model)[["Petal_Width"]],
                    intercept = coef(lm_model)[["(Intercept)"]]),
                color = "red") +
  labs(
    x = "Petal Width",
    y = "Petal Length",
    title = "Linear Regression: Petal Length ~ Petal Width",
    subtitle = "Use Spark.ML linear regression to predict petal length as a function of petal width."
  )

```
## LOGISTIC REGRESSION

```{r}

beaver <- beaver2
beaver$activ <- factor(beaver$activ, labels = c("Non-Active", "Active"))
copy_to(sc, beaver, "beaver", overwrite = TRUE)

beaver_tbl <- tbl(sc, "beaver")

glm_model <- beaver_tbl %>%
  mutate(binary_response = as.numeric(activ == "Active")) %>%
  ml_logistic_regression(binary_response ~ temp)

glm_model

```

